Compiling refinement types to dependent types

### 2020-07-05 tex/paper.tex
A bit nicer equations display

The translation function $[|\ |]$ maps the typing context $\nonterm G$ to some logic:
\begin{equation}
\begin{aligned}
  & [| \emptyset |]                                         && \triangleq \top																						\\
  & [| \nonterm G, x : \{ v : \nonterm B | \nonterm r \} |] && \triangleq [| \nonterm G |] \land [| \{x/v\} \nonterm r |] \\
  & [| \nonterm r_1 \land \nonterm r_2 |]                   && \triangleq [| \nonterm r_1 |] \land [| \nonterm r_2 |]		  \\
  & [| \nonterm{es} |]                                      && \triangleq \text{oracle}(\nonterm{es})                     \\
  & [| \nonterm{es}_1 = \nonterm{es}_2 |]                   && \triangleq \text{oracle}(\nonterm{es}_1 = \nonterm{es}_2)  \\
\end{aligned}
\end{equation}

>>>>

The translation function $[|\ |]$ maps the typing context $\nonterm G$ to some logic:
\begin{equation}
\begin{aligned}
  & [| \emptyset |]                                         && \triangleq && \top																						  \\
  & [| \nonterm G, x : \{ v : \nonterm B | \nonterm r \} |] && \triangleq && [| \nonterm G |] \land [| \{x/v\} \nonterm r |]  \\
  & [| \nonterm r_1 \land \nonterm r_2 |]                   && \triangleq && [| \nonterm r_1 |] \land [| \nonterm r_2 |]      \\
  & [| \nonterm{es} |]                                      && \triangleq && \text{oracle}(\nonterm{es})                      \\
  & [| \nonterm{es}_1 = \nonterm{es}_2 |]                   && \triangleq && \text{oracle}(\nonterm{es}_1 = \nonterm{es}_2)   \\
\end{aligned}
\end{equation}
